NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2018-09-21 Manuscript/manuscriptPGPE.tex
Update PGPE manuscript

\subsection{PE headgroup and glycerol backbone}
\todo{Add results from this discussion: http://nmrlipids.blogspot.com/2017/03/nmrlipids-iv-headgroup-glycerol.html?showComment=1502290977005#c4964787551006026647}
Order parameters from Slipids simulations 
and experiments for DPPE are shown in Fig. \ref{HGorderParametersPE}.
Glycerol backbone order parameters in Slipids are off from experiments,
as already observed previously for PC lipids \cite{botan15}.
Order parameter signs for PE are not experimentally measured yet.
For headgroup the signs are set to give best agreement with simulations
and for glycerol to be consistent with experimental signs for PC.
Order parameter for $\beta$ carbon shows apparent agreement
with experiments. However, the sign of beta order parameter is positive,
in contrast to PC where negative sign was measured. Thus, the the beta order
parameter agrees with experiment with the assumption that its sign is opposite
than for PC. This is yet to be confirmed by experiments.
Order parameter for $\alpha$ carbon is too close to zero, even if the sign
would be correct.

>>>>

\subsection{PE headgroup and glycerol backbone}
\todo{Add results from this discussion: \url{http://nmrlipids.blogspot.com/2017/03/nmrlipids-iv-headgroup-glycerol.html?showComment=1502290977005#c4964787551006026647}}
Order parameters from Slipids simulations 
and experiments for DPPE are shown in Fig. \ref{HGorderParametersPE}.
Glycerol backbone order parameters in Slipids are off from experiments,
as already observed previously for PC lipids \cite{botan15}.
Order parameter signs for PE are not experimentally measured yet.
For headgroup the signs are set to give best agreement with simulations
and for glycerol to be consistent with experimental signs for PC.
Order parameter for $\beta$ carbon shows apparent agreement
with experiments. However, the sign of beta order parameter is positive,
in contrast to PC where negative sign was measured. Thus, the the beta order
parameter agrees with experiment with the assumption that its sign is opposite
than for PC. This is yet to be confirmed by experiments.
Order parameter for $\alpha$ carbon is too close to zero, even if the sign
would be correct.
